\chapter*{Preface\markboth{Preface}{Preface}}\label{[CHAPTER] Preface}
\addcontentsline{toc}{chapter}{Preface}\vspace{-60pt}

This master thesis has been written by Anders Bender, Dennis Bækgaard and Brian Frost during the spring semester of 2016. 
The master thesis details the motivation for the articles (Appendix A \& B)  and the research they surround, a summery of the process of the research, and the conclusions of the articles.
The articles were both written in the spring semester of 2016.

The first article is a combined effort between the groups is101f16 (Anders Bender, Dennis Bækgaard and Brian Frost) and is102f16 (Benjamin Hubert, Michael Fuglsang, Henrik Haxholm). 
The article is largely based of off the 9th semester report, however it has been rewritten in article form as well as substantial changes has been made both with regards to the academic contribution and overall structure for the article, all of which is based on the experienced gained from the 9th semester.

The second article is produced by this our group, but involves an experiment conducted across both groups (IS101F16 and
IS102F16). It is based upon methods and findings from the first article and applies them in a another, more concrete
setting; that of finding usability problems based entirely on physiological data.

\section{Acknowledgement}
We would like to thanks our supervisors Thomas Dyhre Nielsen and Anders Bruun for guidance and constructive feedback throughout the project.
We would also like to thank is102f16 for the collaboration with the first article and the second experiment, and lastly a thank to all the people who helped conduct the experiments.